Adversarial Training of Invariant Features for Speech Recognition

### 2017-03-21 interspeech/paper.tex
fix citation

\section{Conclusion}
\label{sec:discussion}
    This paper presents the application of generative adversarial networks and 
    invariance training for noise robust speech recognition. We show that invariance training 
    helps the ASR system to generalize better to unseen noise conditions and improves 
    the word error rate when a small number of noise types are seen during training. Our 
    experiments show that in contrast to the image recognition task, in speech 
    recognition, the task of the domain classification ($D$) network is harder. Therefore, the 
    gradient of the $L_3$ term in Eq.~\ref{eq:grm} is noisier. Future 
    research includes enhancements to the domain adaptation network while exploring 
    alternative network architectures and invariance-promoting loss functions.

>>>>

\section{Conclusion}
\label{sec:discussion}
    This paper presents the application of generative adversarial networks and 
    invariance training for noise robust speech recognition. We show that invariance training 
    helps the ASR system to generalize better to unseen noise conditions and improves 
    the word error rate when a small number of noise types are seen during training. Our 
    experiments show that, relative to the image recognition tasks reported
    in \citet{ganin2014unsupervised}, the task of the domain classification ($D$) network is
    harder for speech recognition. Therefore, the 
    gradient of the $L_3$ term in Eq.~\ref{eq:grm} is noisier. Future 
    research includes enhancements to the domain adaptation network while exploring 
    alternative network architectures and invariance-promoting loss functions.
